%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Roke - Graduate
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \sectionsep
\runsubsection{Roke}
\descript{| Graduate Engineer - Sensors and Communications }
\location{September 2018 – Present | Romsey, UK}

\vspace{0.5em}
In Dec 2018 I joined a flagship project: designing and delivering a miniaturised software defined radio.
% \vspace{0.25em}
\begin{tightemize}
  \item Design Lead for multiple FPGA firmware modules including algorithm design, testing and implementation. Supporting software written in C++; models written in VHDL, MATLAB and Python.
  \item Prototyped, debugged and implemented SPI and I2C interfaces.
  \item Designed and made cables and circuitry to connect logic analysers, spectrum analysers, and oscilloscopes.
  \item Designed in CAD, organised fabrication, then assembled 8 "Test Jigs" to facilitate software and firmware release testing on target hardware. Identified hardware configuration and modifications required.
  % \item Contributed to design decisions of chosen protocol for peripheral connections (e.g. SPI vs I2C vs SMBus vs CAN bus).
  \item Supporting roles within the project: requirements capture and decomposition; technology platform evaluations; unit and system integration testing.
  \item Solo, and second author of multiple technical white-papers delivered to the customer.
\end{tightemize}

\vspace{0.5em}
Outside of my project I was heavily involved across the business, for example:
% \vspace{0.25em}
\begin{tightemize}
    \item Organising the lunchtime Data Science Club (covering AI and Machine Learning);
    \item Chair of the Healthy Workplace Employee Resource Group;
    \item Delivering outreach activities for Girls in Engineering Day.
\end{tightemize}

\sectionsep
